---
title: "MLC_Project"
author: "Pimm"
date: "28 de enero de 2016"
output: html_document
---

This is my project for the coursera Machine Learning Course.
Our goal is given data collected from barbell lifts performing be able to know if it is well done.
We have to determinate the classe parameter from all data collected by acelerometer.

First we load the librarys we might need:

```{r, echo=FALSE}
library(caret)
library(randomForest)

```

After that we load the data we have alredy download:

```{r, echo=FALSE}
test<-read.csv("pml-testing.csv")
train<-read.csv("pml-training.csv")
```

In a very preliminary analisys we see that the first seven columumns are useless, so we clean it:

```{r}
test1<-test[,-c(1:7)]
train1<-train[,-c(1:7)]
```

In a second preliminar analisys over both data sets we see there are plenty of values NA, and if they are NA
in test data it is difficult that they are useful for prediction.

We clean it taken away NAs columns:

```{r}
rem<-NULL
for (col.nr in 1:dim(test1)[2]){ if (sum(is.na(test1[,col.nr]))) { rem =c(rem, col.nr)}}
test2<-test1[,-rem]
train2<-train1[,-rem]
```

Now it is time to fit our model.
We do it with Random Forest model and for performance reason we split data in 3

```{r}
modfit<-train(classe~.,method="rf",trControl=trainControl(method="cv",number=3),data=train2)
```

Last we clean the test set  (the last column is not necessary) and predict:

```{r}
test3<-test2[,-53]
predict(modfit,newdata=test3)
```

We introduce the predicted output in our given Quitz and we have full success (20/20)!!!
